---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# icepalace

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/ropenscilabs/icepalace/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropenscilabs/icepalace/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of this package is to download entire CRAN-like repositories, for instance R-universe repositories to use the archive as a frozen snapshot.
The frozen snapshot could be kept locally, or for instance served on GitHub Pages.
It might be useful for reproducibility.

The goal of this package is **not** to also snapshot the dependencies of the repository packages that are not in the repository.
If you want such an exhaustive snapshot, use tools like [MRAN](https://mran.microsoft.com/timemachine) or [RStudio Package Manager](https://www.rstudio.com/products/package-manager/).

## Installation

You can install the development version of icepalace from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ropenscilabs/icepalace")
```

## Example

Let's snapshot the r-lib R-universe repository and then install styler from that repo.

```{r example}
library(icepalace)
# In real life do not use a temporary directory :-)
destdir <- withr::local_tempdir()
snapshot_package_repository("https://r-lib.r-universe.dev", destdir = destdir)
fs::dir_tree(destdir)

repo <- sprintf("file:///%s", destdir)
repo
install.packages("styler", repos = c(rlib = repo, CRAN = 'https://cloud.r-project.org'))

pkg_info <- sessioninfo::package_info("styler")
pkg_info[pkg_info$package == "styler",]
```
